---
title: "STA322 Project 2"
author: "Sherry Huang, Eddie Yang"
date: "April 2019"
output:
    pdf_document:
    keep_tex: yes
    latex_engine: xelatex
---

4 factors, full factorial: 2^4 = 16 possible treatment assignments
all low / 0, a, b, c, d, ab, ac, ad, bc, bc, cd, abc, abd, acd, bcd, abcd
5 replicates for each assignment
drop from height of 2 meters

Which factors seeme to be the most important for making helicopters that fly longer?
Is there any evidence that the effect of rotor length differs by leg width?
What would you recommend as the ideal combination to make the helicopter fly long?

####Introduction
  This study aims to examine the factors in desgining a paper helicopter that affect how long it can fly in the air. Specifically, the study focuses on four factors: rotor length, leg length, leg width, and whether or not there is a paper clip at the bottom of the leg. This report includes details of the full factorial experiment design, procedures of data collection, and analysis of estimation results using regression modelling.
  
####Study Design and Data Collection
  Because there are four factors with two levels each, there are a total of $2^4 = 16$ total possible treatment assignments. Since we have no prior knowledge of how these factors interact with each other and thus cannot assume their interaction effects are negligible, we use a full factorial design, which allows us to examine all main effects and interaction effects, for this experiment. We conduct five trials for each of the assignment, which gives us $16 * 5 = 80$ trials in total.
  During each trial, we drop the paper helicopter at the height of exactly two meters, and the flight time as measured from the time the helicopter is dropped from some height until the time it hits the floor. The data is recorded in the table below.
  
    The factors we want to study in this experiment are:
    a: rotor length = 8.5cm (baseline 7.5cm)
    b: leg length = 12.0cm (baseline 7.5cm)
    c: leg width = 5.0cm (baseline 3.2cm)
    d: paper clip on bottom of leg (baseline no paper clip)
  
```{r}
#Randomize treatment assignments
assignments = c(rep("o",5), rep("a",5), rep("b",5), rep("c",5), rep("d",5),
                rep("ab",5), rep("ac",5),rep("ad",5), rep("bc",5), rep("bd",5),
                rep("cd",5), rep("abc",5), rep("abd",5), rep("acd",5), 
                rep("bcd",5), rep("abcd",5))
set.seed(322)
assignments = sample(assignments)
helidata = data.frame(treatments = assignments, 
                      a = NA, b = NA, c = NA, d = NA, time = NA)
write.csv(helidata, file = "helidata.csv")

#Collect data, enter manually, and read file again
heliData = read.csv("helidata.csv", header = TRUE)
#Convert treatments to factors
heliData$treatment = as.factor(heliData$treatments)
heliData$a = as.factor(heliData$a)
heliData$b = as.factor(heliData$b)
heliData$c = as.factor(heliData$c)
heliData$d = as.factor(heliData$d)

#Exploratory Data Analysis
boxplot(heliData$time ~ heliData$treatments, xlab = "Treatment", ylab = "Fly Time")
par(mfrow=c(2,2))   
boxplot(heliData$time ~ heliData$a, xlab = "Rotor Length", ylab = "Fly Time")
boxplot(heliData$time ~ heliData$b, xlab = "Leg Length", ylab = "Fly Time")
boxplot(heliData$time ~ heliData$c, xlab = "Leg Width", ylab = "Fly Time")
boxplot(heliData$time ~ heliData$d, xlab = "Leg Paper Clip", ylab = "Fly Time")

#Regression
regHeli = lm(time ~ a*b*c*d, data = heliData)

summary(regHeli)

knitr::kable(data.frame(estimates = regHeli$coefficients,
                        pvalues = c("<2e-16",0.015218,0.032935,"6.03e-7",0.768488,0.524367,"2.86e-07",
                                    0.002908,0.459207,0.639734,0.000751,0.005955,0.317770,0.003342,
                                    0.496702,0.117377)),
             caption = "Full Factorial Regression Results")

#Residual Plot
boxplot(regHeli$residual~heliData$treatments, xlab = "Treatment", ylab = "Residuals")
#Diagnostic Plots
plot(regHeli)

regHeli$coefficients
regHeli$effects

```
  
####Data Analysis and Results
  
####Discussion
  In our data collection process, there are a few possible sources of error. First, the helicopters are dropped by hand. The person who drops them might apply some force on the helicopter upon releasing, resulting in different initial velocities. Second, because the time is recorded by hand, inaccuracy is inevitable.
  
####Code
```{r}
regHeli = lm(time ~ a*b*c*d, data = heliData)
summary(regHeli)
```

  